Supplement to ``{\mytitle}''

### 2024-03-05 si/ReplicateLee20.Rnw
Removed cached statements

<<Simulate Lee Model 1, echo=FALSE, cache=TRUE>>=
h1_epi <- haiti1()
N_LEE_SIMS <- 20

@@

<<SimulateEpi, echo=FALSE, include=FALSE, message=FALSE, cache=TRUE>>=
h1_end <- haiti1(period = "endemic")

@@

<<plotEndParams, fig.width=7, fig.height=7, fig.align='center', fig.cap="Bivariate distributions of parameter estimates after fitting endemic phase of the Model~1 following the procedure described by Lee et al. (2020). Compare to Figure S9 in the supplement of Lee et al. (2020).", cache=TRUE, echo=FALSE,warning=FALSE>>=
GGally::ggpairs(
  h1LeeStartsEnd,
  columns = c("rho", "tau", "beta1", "nu", "loglik")
)
@

@@

<<plotMod1Sims, echo=FALSE, fig.cap=paste0("Simulations from Model~1 using parameter sets that were generated by running source code provided by Lee et al (2020). Compare to Figure S7 in the supplement of Lee et al. (2020). The upper bound for the likelihood of this model is ", round(mod1_lee_ll), "."), cache=TRUE, fig.width=6.5, fig.height=3.75,warning=FALSE>>=

@@

<<Model2Replication, cache=TRUE, echo=FALSE>>=
h2_epi <- haiti2()
h2_end <- haiti2(region = 'after')

@@

\begin{figure}[!h]
<<plotModel2Rep, cache=TRUE, echo=FALSE, fig.width=6.5, fig.height=4.5>>=
gg_epi <- projections %>%
  filter(date < as.Date("03-01-2014", format = '%m-%d-%Y')) %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = ReportedAll), col = 'black', linetype = 'dashed') +
  geom_line(aes(y = Ctotal), col = 'red', linewidth = 1) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 30000), breaks = seq(0, 30000, 5000)) +
  theme(axis.title.x = element_blank()) +
  ylab("Reported number of cases")

@@

<<Model3Replication, echo=FALSE, cache=TRUE>>=
NSIM <- 500

>>>>

<<Simulate Lee Model 1, echo=FALSE, cache=FALSE>>=
h1_epi <- haiti1()
N_LEE_SIMS <- 20

@@

<<SimulateEpi, echo=FALSE, include=FALSE, message=FALSE, cache=FALSE>>=
h1_end <- haiti1(period = "endemic")

@@

<<plotEndParams, fig.width=7, fig.height=7, fig.align='center', fig.cap="Bivariate distributions of parameter estimates after fitting endemic phase of the Model~1 following the procedure described by Lee et al. (2020). Compare to Figure S9 in the supplement of Lee et al. (2020).", cache=FALSE, echo=FALSE,warning=FALSE>>=
GGally::ggpairs(
  h1LeeStartsEnd,
  columns = c("rho", "tau", "beta1", "nu", "loglik")
)
@

@@

<<plotMod1Sims, echo=FALSE, fig.cap=paste0("Simulations from Model~1 using parameter sets that were generated by running source code provided by Lee et al (2020). Compare to Figure S7 in the supplement of Lee et al. (2020). The upper bound for the likelihood of this model is ", round(mod1_lee_ll), "."), cache=FALSE, fig.width=6.5, fig.height=3.75,warning=FALSE>>=

@@

<<Model2Replication, cache=FALSE, echo=FALSE>>=
h2_epi <- haiti2()
h2_end <- haiti2(region = 'after')

@@

\begin{figure}[!h]
<<plotModel2Rep, cache=FALSE, echo=FALSE, fig.width=6.5, fig.height=4.5>>=
gg_epi <- projections %>%
  filter(date < as.Date("03-01-2014", format = '%m-%d-%Y')) %>%
  ggplot(aes(x = date)) +
  geom_line(aes(y = ReportedAll), col = 'black', linetype = 'dashed') +
  geom_line(aes(y = Ctotal), col = 'red', linewidth = 1) +
  theme_bw() +
  scale_y_continuous(limits = c(0, 30000), breaks = seq(0, 30000, 5000)) +
  theme(axis.title.x = element_blank()) +
  ylab("Reported number of cases")

@@

<<Model3Replication, echo=FALSE, cache=FALSE>>=
NSIM <- 500
